Paper_analyses

### 2021-11-15 Paper_Analyses_subj_obje_arousal.Rmd
filter out missigngness

clustering<- db_full6new_hr_fix_stim_nt1.1%>%
  subset(Bio_Mean_HR_dif_outl == "not outlier")%>%
  select(
                    c(Bio_Mean_HR_dif, pup_basCor, BIO_CDA.PhasicMax, BIO_CDA.ISCR, BIO_TTP.AmpSum,
                      BIO_CDA.SCR, arousal, valence, ArousalMean, ValenceMean, stimIAPS, tNo, TAS, AQ, Age,
                      gender, ssid, stimDescription))

@@

clustering_new_pre_PCA<- select(clustering_new, c(ssid, TAS, AQ, stimIAPS2, 
                                                  pup_basCor,Bio_Mean_HR_dif,
                                                  log_BIO_CDA.PhasicMax, arousal,
                                                  valence))
db_forPCA<- data.table::dcast(setDT(clustering_new_pre_PCA), 
                    ssid + TAS+AQ ~ stimIAPS2, value.var = c('pup_basCor',
                'Bio_Mean_HR_dif', 'log_BIO_CDA.PhasicMax', 'arousal', 'valence'))

>>>>

```{r}
library(tidyverse)
db_full6new_hr_fix_stim_nt1.1

clustering<- db_full6new_hr_fix_stim_nt1.1%>%
  subset(Bio_Mean_HR_dif_outl == "not outlier")%>%
  select(
                    c(Bio_Mean_HR_dif, pup_basCor, BIO_CDA.PhasicMax, BIO_CDA.ISCR, BIO_TTP.AmpSum,
                      BIO_CDA.SCR, arousal, valence, ArousalMean, ValenceMean, stimIAPS, tNo, TAS, AQ, Age,
                      gender, ssid, stimDescription, fix_count, mean_fix_dur))

@@

# clustering_new$=
# clustering
clustering_new_pre_PCA<- select(clustering, c(ssid, TAS, AQ, stimIAPS2,
                                              stimDescription, 
                                                  pup_basCor,Bio_Mean_HR_dif,
                                                  log_BIO_CDA.PhasicMax, arousal,
                                                  valence, fix_count, mean_fix_dur))

clustering_new_pre_PCA

clustering_new_pre_PCA$stim_descr<- paste0(clustering_new_pre_PCA$stimIAPS2, 
                                           paste0(clustering_new_pre_PCA$stimDescription))

clustering_new_pre_PCA$stim_descr

clustering_new_pre_PCA
db_forPCA<- data.table::dcast(setDT(clustering_new_pre_PCA), 
                    ssid + TAS+AQ ~ stim_descr, value.var = c('pup_basCor',
                'Bio_Mean_HR_dif', 'log_BIO_CDA.PhasicMax', 'arousal', 'valence', 
                'fix_count', 'mean_fix_dur'))

View(db_forPCA)
colnames(db_forPCA)

# 
# start with just physio stuff

all.data<- db_forPCA

# count NAS on the important variables
# pupufirst(

colnames(all.data[,61: (61+56)])
all.data$per_ssid_pupil_loss_perc <- (rowSums(is.na(all.data[,4:60]))/56)*100 # pupil
# rowSums(is.na(all.data[,4:60]))
all.data$per_ssid_hr_loss_perc<-  (rowSums(is.na(all.data[,61: (61+56)]))/56)*100 # heart rate
all.data$per_ssid_scr_loss_perc<- (rowSums(is.na(all.data[,(61+56):(61+56+56)]))/56)*100 # scr

# columns

cols_belowmissingthresh <- which(colSums(is.na(all.data))/nrow(all.data) < .8)
  # all.data%>%
colSums(is.na(all.data))/nrow(all.data)

ncol(all.data)
# select columsn that don't have a a lot of missingness
all.data1<- all.data%>%
  select(cols_belowmissingthresh)

all.data$TAS_mediansplit<- if_else(all.data$TAS> median(all.data$TAS), "High", "Low")
all.data$AQ_mediansplit<- if_else(all.data$AQ> median(all.data$AQ), "High", "Low")
 # design
var.design_asd <- as.factor(all.data$Group)
var.design_aq <- as.factor(all.data$AQ_mediansplit)
var.design_tas <- as.factor(all.data$TAS_mediansplit)
colnames(all.data)

var.data <- all.data[,c(6:172)]

var.PCA.inf_asd <-InPosition::epPCA.inference.battery(var.data, 
                                       scale = FALSE, 
                                       center = FALSE, 
                                       DESIGN = var.design_asd, 
                                       make_design_nominal = TRUE, 
                                       graphs = TRUE, k = 0, 
                                       test.iters = 1000, 
                                       constrained = FALSE, 
                                       critical.value = 2)
